---
title: "Lab 00 - Hello IDS!"
author: "Euan Riach"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Romi", "Barney", "Duncan", 
           "Karan", "Matteo"),
  github_username = c("romikaushik", "bmccreery", "DJones2334", 
                      "Karan-s06", "MatteoSmirney"), 
  colour = c("Green", "Green", "Green", 
             "Purple", "Blue"),
  hobby = c("Swimming", "Motorsport", "MMA", 
            "Badminton", "Formula 1"),
  favourite_number = c(9, 4, 1, 3, 9)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows everyone's favourite number on a graph and how big the numbers are relative to one another.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "Favourite Number against Github Username")
```

#Labs allows a change in axis labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Allow people to chose from specific options so different spellings or names of the same activity don't get counted and dispayed separately from one another.
